---
title: "ESM 204 HW 2"
author: "Sam Rozal, Virginia Pan, Kat Orellana"
date: "4/25/2022"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(tidyr)
library(here)
library(janitor)
library(lubridate)
library(kableExtra)
```

```{r}
water_districts <- read_csv(here("data", "Water_Districts.csv"))
```
1. For each irrigation district, plot the marginal abatement cost data (from the data provided) and estimate a linear regression model with zero intercept. These estimated linear regressions will be your estimates of the marginal abatement cost curve (one for each irrigation district), which you will use for the remainder of this analysis.

```{r}
#plot abatement for Kern county
ggplot(data=water_districts, aes(x=Reduction, y=MC_Kern))+
  geom_point()+
  labs(x="Reduction",
       y= "Marginal Cost Of Abatement",
       title = "Cost of Abatement in Kern County")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))
```
```{r}
#Find linear regression model for Kern county 
kern_lm <- lm(MC_Kern ~ 0 + Reduction, data=water_districts)
```
Marginal Cost for Kern County = 2.286A

```{r}
#fitting line for kern 
kern_baseline <- 150
kern_data <- tibble(Reduction = 0:150)
predicted_mc <- predict(kern_lm, newdata=kern_data)
kern_data <- kern_data %>% mutate(predicted_mc=predicted_mc)
```

```{r}
#plotting with predicted line 
ggplot(water_districts, aes(x=Reduction, y=MC_Kern))+
  geom_point()+
  geom_line(data=kern_data, aes(x=Reduction, y=predicted_mc))
```

```{r}
#plot abatement for Mojave county
ggplot(data=water_districts, aes(x=Reduction, y=MC_Mojave))+
  geom_point()+
  labs(x="Reduction",
        y= "Marginal Cost Of Abatement",
       title = "Cost of Abatement in Mojave County")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))
```

```{r}
#Find linear regression model for Mojave county 
mojave_lm <- lm(MC_Mojave ~ 0 + Reduction, data=water_districts)
mojave_lm_tidy <- broom::tidy(mojave_lm)
summary(mojave_lm)

mojave_lm
```
MC(A) for Mojave County = 3.804A

```{r}
#fitting line for Mojave 
mojave_baseline <- 140
mojave_data <- tibble(Reduction = 0:140)
predicted_mc <- predict(mojave_lm, newdata=mojave_data)
mojave_data <- mojave_data %>% mutate(predicted_mc=predicted_mc)
```

```{r}
#plotting with predicted line 
ggplot(water_districts, aes(x=Reduction, y=MC_Mojave))+
  geom_point()+
  geom_line(data=mojave_data, aes(x=Reduction, y=predicted_mc))
```

```{r}
#plot the abatement curve for antelope
ggplot(data=water_districts, aes(x=Reduction, y=MC_Antelope))+
  geom_point()+
  labs(x="Reduction",
        y= "Marginal Cost Of Abatement",
       title = "Cost of Abatement in Antelope County")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))
```

```{r}
antelope_lm <- lm(MC_Antelope ~ 0 + Reduction, data=water_districts)
antelope_lm_tidy <- broom::tidy(antelope_lm)

antelope_lm
```
MC(A) for Antelope County = 2.858A

```{r}
#fitting line for antelope 
antelope_baseline <- 220
antelope_data <- tibble(Reduction = 0:220)
predicted_mc <- predict(antelope_lm, newdata=antelope_data)
antelope_data <- antelope_data %>% mutate(predicted_mc=predicted_mc)
```

```{r}
#plotting with predicted line 
ggplot(water_districts, aes(x=Reduction, y=MC_Antelope))+
  geom_point()+
  geom_line(data=antelope_data, aes(x=Reduction, y=predicted_mc))
```


```{r}
ggplot(data=water_districts, aes(x=Reduction, y=MC_Ventura))+
  geom_point()+
  labs(x="Reduction",
        y= "Marginal Cost Of Abatement",
       title = "Cost of Abatement in Ventura County")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))
```
```{r}
ventura_lm <- lm(MC_Ventura ~ 0 + Reduction, data=water_districts)
ventura_lm_tidy <- broom::tidy(ventura_lm)

ventura_lm
```
MC(A) for Ventura County = 1.776A

```{r}
#fitting line for Ventura 
ventura_baseline <- 245
ventura_data <- tibble(Reduction = 0:245)
predicted_mc <- predict(ventura_lm, newdata=ventura_data)
ventura_data <- ventura_data %>% mutate(predicted_mc=predicted_mc)
```

```{r}
#plotting with predicted line 
ggplot(water_districts, aes(x=Reduction, y=MC_Ventura))+
  geom_point()+
  geom_line(data=ventura_data, aes(x=Reduction, y=predicted_mc))
```

# 2. Using your estimated marginal abatement cost curves, derive each district’s demand curve for water.In other words, how much would each district be willing to pay for the right to use the first AF of water,second AF, etc.? Plot each district’s demand curve on a single graph. Which sector is willing to pay the most for the first AF of water?

## Kern County:
```{r}
#derive the demand curve for Kern County 
#define demand or use as baseline (no policy) - Abatement
kern_data <- kern_data %>% mutate(water_demand=kern_baseline-Reduction)
```

To calculate demand for Kern County:

P= 2.286(A) and A= E0-E, where E0=150 AF

P= 2.286(E0-E)

P= 2.286(150-E)

P= 342.9 - 2.286E

Marginal Demand for Kern County = 342.9 - 2.286E

```{r}
#plot the demand for Kern County
ggplot(kern_data, aes(x=water_demand,y=predicted_mc))+
  geom_line() +
  labs(x="Water Use (Acre Foot)",
       y= "Price (Dollars per Acre Foot)",
       title = "Water Demand Curve for Kern County")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))
```

### Mojave County:
```{r}
#derive demand curve for Mojave county
#define demand or use as baseline (no policy) - Abatement
mojave_data <- mojave_data %>% mutate(water_demand=mojave_baseline-Reduction)
```
To calculate demand for Mojave County:

P= 3.804(A) and A= E0-E, where E0=140 AF

P= 3.804(E0-E)

P= 3.804(140-E)

P= 532.56 - 3.804E

```{r}
#plot the demand for Mojave County
ggplot(mojave_data, aes(x=water_demand,y=predicted_mc))+
  geom_line() +
  labs(x="Water Use (Acre Foot)",
       y= "Price (Dollars per Acre Foot)",
       title = "Water Demand Curve for Mojave County")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))
```

### Antelope County:
```{r}
#derive demand curve for Antelope County
#define demand or use as baseline (no policy) - Abatement
antelope_data <- antelope_data %>% mutate(water_demand=antelope_baseline-Reduction)
```

To calculate demand for Antelope County:

P= 2.858(A) and A= E0-E, where E0=220 AF

P= 2.858(E0-E)

P= 2.858(220-E)

P= 628.76 - 2.858E

```{r}
#plot the demand curve for Antelope County
ggplot(antelope_data, aes(x=water_demand,y=predicted_mc))+
  geom_line() +
  labs(x="Water Use (Acre Foot)",
       y= "Price (Dollars per Acre Foot)",
       title = "Water Demand Curve for Antelope County")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))
```

### Ventura County:
```{r}
#derive demand curve for Ventura County
#define demand or use as baseline (no policy) - Abatement
ventura_data <- ventura_data %>% mutate(water_demand=ventura_baseline-Reduction)
```

To calculate demand for Ventura County:

  P= 1.776(A) and A= E0-E, where E0=245 AF
  
  P= 1.776(E0-E)
  
  P= 1.776(245-E)
  
  P= 435.12 - 1.776E

```{r}
#plot the demand for Ventura County
ggplot(ventura_data, aes(x=water_demand,y=predicted_mc))+
  geom_line() +
  labs(x="Water Use (Acre Foot)",
       y= "Price (Dollars per Acre Foot)",
       title = "Water Demand Curve for Ventura County")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))
```



```{r}
#using demand data from Kern and Mojave, join into one data set for plotting 
joined_demand <- bind_rows("Mojave" = mojave_data,
                           "Kern" = kern_data, 
                           "Antelope" = antelope_data,
                           "Ventura" = ventura_data,
                           .id="Districts")


ggplot(data=joined_demand, aes(x=water_demand, y=predicted_mc))+
  geom_line(aes(color=Districts)) +
  labs(x="Water Use (Acre Foot)",
       y= "Price (Dollars per Acre Foot)",
       title = "Water Demand")+
  theme(legend.background= element_rect(fill= "light blue"))+
  theme(plot.background = element_rect(fill="azure2")) +
  theme(panel.background = element_rect(fill="aliceblue"))



#this is what sandy did in office hours but it didnt work so I did a ggplot : plot(data = joined_demand, aes(x=water_demand, y=predicted_mc, color="Districts"))+ geom_line()

```


Antelope irrigation district is willing to pay the most for the first acre-foot of water. 

## How to Solve 3A
Here you will analyze three alternative policies for reducing water use among these irrigation districts.In total, these irrigation districts will need to reduce water consumption from the current 755 AF down to 500 AF. For each intervention listed below, perform the following calculations: (1) calculate the stringency of the policy (defined below for each intervention) required to achieve the 500 AF target, (2) calculate the total cost of meeting the target using that approach, (3) calculate the cost to each district, and (4) calculate the tax revenue generated.

a. Cap without trade. Reduce each district’s water use by the same fraction (e.g., 1/3 of current baseline use), so the 500 AF target is met. Trade is not allowed. Stringency is defined as the magnitude of the fraction.

- Using the baseline in each of the four cities, I set up an equation where the same fraction for each city times each city's baseline sums to 225. (225 is the amount of abatement that is needed (755-500))
- p*150 + p*145 + p*220 + p*245 = 255
- p = 0.338
- Each city will reduce their water usage by 0.338 to achieve the policy [0.338 stringency]
- No tax revenue generated

Kern county:
Abatement = baseline x 0.338
Abatement = 150 X 0.338
Abatement = 50.7

Mojave County:
Abatement = baseline x 0.338
Abatement = 140 X 0.338
Abatement = 47.32

Antelope County:
Abatement = baseline x 0.338
Abatement = 220 X 0.338
Abatement = 74.36

Ventura County:
Abatement = baseline x 0.338
Abatement = 245 X 0.338
Abatement = 82.81

```{r}
quantity_abate = 50

#defining function
calc_cost <- function(lm_mod, quantity_abate){
  estimated_cost = lm_mod$coefficients[1]*quantity_abate
  total_cost = 0.5 * quantity_abate * estimated_cost
  return(total_cost[[1]])
}

#what is the total cost of kern were to abate 117 unit?
kern_cost <- calc_cost(kern_lm, quantity_abate = 50.7)

mojave_cost <- calc_cost(mojave_lm, quantity_abate = 47.32)

antelope_cost <- calc_cost(antelope_lm, quantity_abate = 74.36)

ventura_cost <- calc_cost(ventura_lm, quantity_abate = 82.81)

kern_cost
mojave_cost
antelope_cost
ventura_cost

total_cost <- kern_cost + mojave_cost + antelope_cost + ventura_cost
total_cost

```
Total cost is: `r total_cost`
Kern abatement cost is: `r kern_cost`
Mojave abatement cost is: `r mojave_cost`
Antelope abatement cost is: `r antelope_cost`
Ventura abatement cost is: `r ventura_cost`

b. Tax on water use. A single tax is implemented on all water use in each of the four districts, such that water use is reduced to the 500 AF target. Stringency is defined as the magnitude of the tax.

To calculate the tax, I first need to find the Aggregated Marginal Cost equation. 
- This is done by first converting all of my marginal cost equations to solve for the Q variable because I will be horizontally summing and the Q value is the X value. 

Kern County : P=2.286Q
- Q(kern) = (1/2.286)P

Mojave County: P=3.804Q
- Q(mojave) = (1/3.804)P

Antelope County: P=2.858Q
- Q(antelope) = (1/2.858)P

Ventura County: P=1.776Q
- Q(ventura) = (1/1.776)P

Q(agg) = Q(kern) + Q(mojave) + Q(antelope) + Q(ventura)
Q(agg) = (1/2.286)P + (1/3.804)P + (1/2.858)P + (1/1.776)P
Q(agg) = 1.613(P)

Now, to find P* at the Q* value, I plug in 255 as Qagg, because this is the amount of abatement that we want and then solve for P

255 = 1.613(P)
P = 158.09
P* = 158.09

Now, we need to calculate the Q value (quantity abated) associated with this P for each district/county's marginal demand curve. To do this, we plug in P = 158.062 into each of the marginal cost curves. 


Kern County :
- Q(kern) = (1/2.286)(158.09)
- Q(kern) = 69.14

Mojave County: P=3.804Q
- Q(mojave) = (1/3.804)(158.09)
- Q(mojave) = 41.56

Antelope County: P=2.858Q
- Q(antelope) = (1/2.858)(158.09)
- Q(antelope) = 55.31

Ventura County: P=1.776Q
- Q(ventura) = (1/1.776)(158.09)
- Q(ventura) = 89.01

```{r}
kern_cost_b <- calc_cost(kern_lm, quantity_abate = 69.14)

mojave_cost_b <- calc_cost(mojave_lm, quantity_abate = 41.56)

antelope_cost_b <- calc_cost(antelope_lm, quantity_abate = 55.31)

ventura_cost_b <- calc_cost(ventura_lm, quantity_abate = 89.01)

kern_cost_b
mojave_cost_b
antelope_cost_b
ventura_cost_b

total_cost_b <- kern_cost_b + mojave_cost_b + antelope_cost_b + ventura_cost_b
total_cost_b

```
Total abatement cost with tax is: `r total_cost_b`
Kern abatement cost with tax is: `r kern_cost_b`
Mojave abatement cost with tax is: `r mojave_cost_b`
Antelope abatement cost with tax is: `r antelope_cost_b`
Ventura abatement cost with tax is: `r ventura_cost_b`

Stringency (magnitude of the tax) is: $158.09 

```{r}
#calculate the revenue for tax 1
tax1 = 158.09

#write a function
calc_revenue <- function(tax_val, baseline,quantity_abate){
  revenue <- (tax_val * (baseline-quantity_abate))
  return(revenue)
}

revnue_kern <- calc_revenue(tax1, baseline=140,quantity_abate=69.14)
revnue_mojave <- calc_revenue(tax1, baseline=150,quantity_abate=41.56)
revnue_antelope <- calc_revenue(tax1, baseline=220,quantity_abate=55.31)
revnue_ventura <- calc_revenue(tax1, baseline=240,quantity_abate=89.01)

revnue_kern 
revnue_mojave 
revnue_antelope 
revnue_ventura 

total_tax_revenue <- revnue_kern + revnue_antelope + revnue_ventura + revnue_mojave
total_tax_revenue
#double check gov revenue calculations
#tax is on the amount of water used! 
total_quantity_used = 500
total_tax_revenue2 = total_quantity_used*tax1
total_tax_revenue2
```
Total government revenue generated from tax: $`r total_tax_revenue`


c. Cap and trade. Cap water use as in part (a), but after those caps are set, allow trade across districts. How much water is used by each district after trade? Stringency is the same as in part (a).


For Cap and Trade, we set the initial Q values for each of the four districts so that it is the same as in part (a) so Kern abates 50.07 AF, Mojave abates 47.32 AF, Antelope abates 74.36 AF, and Ventura abates 82.81 AF. However because trading is allowed, the districts will buy and sell their water rights, to reach the socially optimal point which is what we found under part b. Therefore in the end, Kern abates 69.14 AF, Mojave abates 41.56 AF, Antelope abates 55.31 AF, and Ventura abates 89.01 AF.

The cost therefore, should be the same as in part b


```{r}
kern_cost_b <- calc_cost(kern_lm, quantity_abate = 69.14)

mojave_cost_b <- calc_cost(mojave_lm, quantity_abate = 41.56)

antelope_cost_b <- calc_cost(antelope_lm, quantity_abate = 55.31)

ventura_cost_b <- calc_cost(ventura_lm, quantity_abate = 89.01)

kern_cost_b
mojave_cost_b
antelope_cost_b
ventura_cost_b
```

However there is the additional benefit that each district will get due to either revenue that they get from selling, or from getting to use more water than they would have under the original cap. This is calculated below:

```{r}
#find the estimated q value both before and after trade
estimated_cost <- function(lm_mod, quantity_abate){
  (estimated_cost = lm_mod$coefficients[1]*quantity_abate)
  return(estimated_cost)
}

kern_before_trade <- estimated_cost(kern_lm,50.07)
kern_after_trade <- estimated_cost(kern_lm, 69.14)

mojave_before_trade <-estimated_cost(mojave_lm,47.32)
mojave_after_trade <-estimated_cost(mojave_lm,41.56)

antelope_before_trade <-estimated_cost(antelope_lm,74.36)
antelope_after_trade <-estimated_cost(antelope_lm,55.31)

ventura_before_trade <-estimated_cost(ventura_lm,82.81)
ventura_after_trade <-estimated_cost(ventura_lm,89.01)

kern_before_trade
kern_after_trade
mojave_before_trade
mojave_after_trade
antelope_before_trade
antelope_after_trade
ventura_before_trade
ventura_after_trade
```

```{r}
additional_benefit <- function(p_before_trade,p_after_trade,q_before_trade,q_after_trade){
  (additional_benefit =(0.5)*(p_before_trade-p_after_trade)*(q_before_trade-q_after_trade))
  return(additional_benefit)
}

additional_benefit_kern <-additional_benefit(kern_before_trade, kern_after_trade, 50.07, 69.14)
additional_benefit_mojave <- additional_benefit(mojave_before_trade, mojave_after_trade,47.32,41.56)
additional_benefit_antelope <- additional_benefit(antelope_before_trade, antelope_after_trade,74.36,55.31)
additional_benefit_ventura <- additional_benefit(ventura_before_trade, ventura_after_trade,82.81,89.01)

additional_benefit_kern
additional_benefit_mojave
additional_benefit_antelope
additional_benefit_ventura
```
Now we can get the total cost by subtracting the cost we got in a, minus the additional benefit.


```{r}
#kern county cost:
total_cost_kern <- kern_cost - additional_benefit_kern

total_cost_mojave <- mojave_cost - additional_benefit_mojave

total_cost_antelope <- antelope_cost - additional_benefit_antelope

total_cost_ventura <- ventura_cost - additional_benefit_ventura

total_cost_kern
total_cost_mojave
total_cost_antelope
total_cost_ventura

total_cost_all <- total_cost_kern + total_cost_mojave + total_cost_antelope + total_cost_ventura
total_cost_all
```
Stringency is the same as in part 1:  0.338

Total cost under cap and trade is: $ `r total_cost_all`

Total cost under cap and trade for Kern is: $ `r total_cost_kern`

Total cost under cap and trade for Mojave is: $ `r total_cost_mojave`

Total cost under cap and trade for Antelope is: $ `r total_cost_antelope`

Total cost under cap and trade for Ventura is: $ `r total_cost_ventura`

No Tax revenue is generated under cap and trade 

```{r}
#calculate by hand
#baseline = c(150, 140, 220, 245)

#a single fraction multiplied by these numbers that sum to 755-500 = 225

#deductions <- function(p) {p*150+p*145+p*220+p*245 = 255}
#p= 0.338
#solve(deductions)
```

```{r}
#A function to compute the costs for a district's abatement given the abatement number
quantity_abate = 50
lm_mod=kern_lm

#defining function
calc_cost <- function(lm_mod, quantity_abate){
  estimated_cost = lm_mod$coefficients[1]*quantity_abate
  total_cost = 0.5 * quantity_abate * estimated_cost
  return(total_cost[[1]])
}

#what is the total cost of kern were to abate 117 unit?
calc_cost(kern_lm, quantity_abate = 117)

#Q3a Kern abated
calc_cost(kern_lm, quantity_abate = 50.7)
```

# Number 4
4. A severe drought hits California, and it is necessary to reduce water use from 500 AF down to 300 AF. Your job is to estimate the cost of the drought (i.e., the cost of reducing water use from 500 AF to 300 AF) to each irrigation district under each policy. Considering the entire jump from status quo (755 AF) to the drought (300 AF), which policy is preferred by each irrigation district? How does your answer depend on how rights are allocated to each district (in policies (a) and (c))2?

a. Cap without trade. Reduce each district’s water use by the same fraction (e.g., 1/3 of current baseline use), so the 300 AF target is met. Trade is not allowed. Stringency is defined as the magnitude of the fraction.

- Using the baseline in each of the four cities, I set up an equation where the same fraction for each city times each city's baseline sums to 225. (225 is the amount of abatement that is needed (755-300))
- p*150 + p*145 + p*220 + p*245 = 455
- p = 0.599
- Each city will reduce their water usage by 0.599 to achieve the policy [0.599 stringency]
- No tax revenue generated

Kern county:
Abatement = baseline x 0.599
Abatement = 150 X 0.599
Abatement = 89.85

Mojave County:
Abatement = baseline x 0.599
Abatement = 140 X 0.599
Abatement = 83.86

Antelope County:
Abatement = baseline x 0.599
Abatement = 220 X 0.599
Abatement = 131.78

Ventura County:
Abatement = baseline x 0.599
Abatement = 245 X 0.338
Abatement = 146.76

```{r}

#defining function
calc_cost <- function(lm_mod, quantity_abate){
  estimated_cost = lm_mod$coefficients[1]*quantity_abate
  total_cost = 0.5 * quantity_abate * estimated_cost
  return(total_cost[[1]])
}

#what is the total cost of kern were to abate 117 unit?
kern_cost_4 <- calc_cost(kern_lm, quantity_abate = 89.85)

mojave_cost_4<- calc_cost(mojave_lm, quantity_abate = 83.86)

antelope_cost_4 <- calc_cost(antelope_lm, quantity_abate = 131.78)

ventura_cost_4 <- calc_cost(ventura_lm, quantity_abate = 146.76)

kern_cost_4
mojave_cost_4
antelope_cost_4
ventura_cost_4

total_cost_4 <- kern_cost_4 + mojave_cost_4 + antelope_cost_4 + ventura_cost_4
total_cost_4

```
Total cost is: `r total_cost_4`
Kern abatement cost is: `r kern_cost_4`
Mojave abatement cost is: `r mojave_cost_4`
Antelope abatement cost is: `r antelope_cost_4`
Ventura abatement cost is: `r ventura_cost_4`

b. Tax on water use. A single tax is implemented on all water use in each of the four districts, such that water use is reduced to the 300 AF target. Stringency is defined as the magnitude of the tax.

To calculate the tax, I first need to find the Aggregated Marginal Cost equation.
- This is done by first converting all of my marginal cost equations to solve for the Q variable because I will be horizontally summing and the Q value is the X value.

Kern County : P=2.286Q
- Q(kern) = (1/2.286)P

Mojave County: P=3.804Q
- Q(mojave) = (1/3.804)P

Antelope County: P=2.858Q
- Q(antelope) = (1/2.858)P

Ventura County: P=1.776Q
- Q(ventura) = (1/1.776)P

Q(agg) = Q(kern) + Q(mojave) + Q(antelope) + Q(ventura)
Q(agg) = (1/2.286)P + (1/3.804)P + (1/2.858)P + (1/1.776)P
Q(agg) = 1.613(P)

Now, to find P* at the Q* value, I plug in 455 as Qagg, because this is the amount of abatement that we want and then solve for P

455 = 1.613(P)
P = 282.08
P* = 282.08

Now, we need to calculate the Q value (quantity abated) associated with this P for each district/county's marginal demand curve. To do this, we plug in P = 158.062 into each of the marginal cost curves.


Kern County :
- Q(kern) = (1/2.286)(282.08)
- Q(kern) = 123.39

Mojave County: P=3.804Q
- Q(mojave) = (1/3.804)(282.08)
- Q(mojave) = 74.15

Antelope County: P=2.858Q
- Q(antelope) = (1/2.858)(282.08)
- Q(antelope) = 98.70

Ventura County: P=1.776Q
- Q(ventura) = (1/1.776)(282.08)
- Q(ventura) = 158.83

```{r}
kern_cost_b_4 <- calc_cost(kern_lm, quantity_abate = 123.39)

mojave_cost_b_4 <- calc_cost(mojave_lm, quantity_abate = 74.15)

antelope_cost_b_4 <- calc_cost(antelope_lm, quantity_abate = 98.70)

ventura_cost_b_4 <- calc_cost(ventura_lm, quantity_abate = 158.83)

kern_cost_b_4
mojave_cost_b_4
antelope_cost_b_4
ventura_cost_b_4

total_cost_b_4 <- kern_cost_b_4 + mojave_cost_b_4 + antelope_cost_b_4 + ventura_cost_b_4
total_cost_b_4

```

```{r}
#calculate the revenue

#write a function
calc_revenue <- function(baseline,quantity_abate){
  revenue <- (282.08 * (baseline-quantity_abate))
  return(revenue)
}

revnue_kern_4 <- calc_revenue(baseline=140,quantity_abate=123.39)
revnue_mojave_4 <- calc_revenue(baseline=150,quantity_abate=74.15)
revnue_antelope_4 <- calc_revenue(baseline=220,quantity_abate=98.70)
revnue_ventura_4 <- calc_revenue(baseline=245,quantity_abate=158.83)

revnue_kern_4
revnue_mojave_4
revnue_antelope_4
revnue_ventura_4

```

c. Cap and trade. Cap water use as in part (a), but after those caps are set, allow trade across districts. How much water is used by each district after trade? Stringency is the same as in part (a).


For Cap and Trade, we set the initial Q values for each of the four districts so that it is the same as in part (a) so Kern abates 50.07 AF, Mojave abates 47.32 AF, Antelope abates 74.36 AF, and Ventura abates 82.81 AF. However because trading is allowed, the districts will buy and sell their water rights, to reach the socially optimal point which is what we found under part b. Therefore in the end, Kern abates 69.14 AF, Mojave abates 41.56 AF, Antelope abates 55.31 AF, and Ventura abates 89.01 AF.

However there is the additional benefit that each district will get due to either revenue that they get from selling, or from getting to use more water than they would have under the orgninal cap. This is calculated below:

```{r}
#find the estimated p value both before and after trade
estimated_cost <- function(lm_mod, quantity_abate){
  (estimated_cost = lm_mod$coefficients[1]*quantity_abate)
  return(estimated_cost)
}

kern_before_trade_4 <- estimated_cost(kern_lm,89.85)
kern_after_trade_4<- estimated_cost(kern_lm, 123.39)

mojave_before_trade_4 <-estimated_cost(mojave_lm,83.86)
mojave_after_trade_4 <-estimated_cost(mojave_lm,74.15)

antelope_before_trade_4 <-estimated_cost(antelope_lm,131.78)
antelope_after_trade_4 <-estimated_cost(antelope_lm,98.70)

ventura_before_trade_4 <-estimated_cost(ventura_lm,146.76)
ventura_after_trade_4 <-estimated_cost(ventura_lm,158.83)

kern_before_trade_4
kern_after_trade_4
mojave_before_trade_4
mojave_after_trade_4
antelope_before_trade_4
antelope_after_trade_4
ventura_before_trade_4
ventura_after_trade_4
```

```{r}
additional_benefit <- function(p_before_trade,p_after_trade,q_before_trade,q_after_trade){
  (additional_benefit =(0.5)*(p_before_trade-p_after_trade)*(q_before_trade-q_after_trade))
  return(additional_benefit)
}

additional_benefit_kern_4 <-additional_benefit(kern_before_trade_4, kern_after_trade_4, 89.85, 123.39)
additional_benefit_mojave_4<- additional_benefit(mojave_before_trade_4, mojave_after_trade_4,83.86,74.15)
additional_benefit_antelope_4<- additional_benefit(antelope_before_trade_4, antelope_after_trade_4, 131.78,98.70)
additional_benefit_ventura_4 <- additional_benefit(ventura_before_trade_4, ventura_after_trade_4,146.76,158.83)

additional_benefit_kern_4
additional_benefit_mojave_4
additional_benefit_antelope_4
additional_benefit_ventura_4
```
Now we can get the total cost by subtracting the cost we got in a, minus the additional benefit.


```{r}
#kern county cost:
total_cost_kern_4 <- kern_cost_4 - additional_benefit_kern_4

total_cost_mojave_4 <- mojave_cost_4 - additional_benefit_mojave_4

total_cost_antelope_4 <- antelope_cost_4 - additional_benefit_antelope_4

total_cost_ventura_4 <- ventura_cost_4 - additional_benefit_ventura_4

total_cost_kern_4
total_cost_mojave_4
total_cost_antelope_4
total_cost_ventura_4

total_cost_all_4 <- total_cost_kern_4 + total_cost_mojave_4 + total_cost_antelope_4 + total_cost_ventura_4
total_cost_all_4
```


```{r}
#calculate by hand
#baseline = c(150, 140, 220, 245)

#a single fraction multiplied by these numbers that sum to 755-500 = 225

#deductions <- function(p) {p*150+p*145+p*220+p*245 = 255}
#p= 0.338
#solve(deductions)
```

